Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-07-17 Response.tex

In order to improve the clarity and reduce confusion, we have added some additional detail to the discussion of the \Poincare map to the manuscript.
This addition has been copied below.
\begin{correction}
\Poincare maps are a useful tool in the analysis of the flow near periodic orbits in the three-body problem.
We let \( \Sigma \) define a hypersurface of section chosen such that all trajectories in the vicinity of a state \( \vecbf{q} \in \Sigma \) cross \( \Sigma \) transversely and in the same direction.
A \Poincare map, \( P(\vecbf{q}) = \phi(T;\vecbf{q}) \), maps the state of a trajectory from one intersection to the next.
Choosing a section in this manner results in a \Poincare section as shown in~\cref{fig:poincare_map}.
In~\cref{fig:poincare_map} we show two examples of periodic trajectories intersecting the \Poincare section. 
Periodic solutions will appear as fixed points on the section, such as \( q_0, q_1 \) in~\cref{fig:poincare_map}, while stable or unstable trajectories become clearly visible by viewing successive intersections of the section.
This allows for greater insight into the stability and dynamics of periodic solutions of a dynamic system as a fixed point on the \Poincare section corresponds to a periodic orbit while movement on the section is associate with the stability of neighboring trajectories. 
\end{correction}

\item
    \begin{itshape}
Figure 6 is also very unclear.  Is phi supposed to be \texttt{theta\_d}?  Is the bounding curve specifically circular, or should it be a more general shape?
\end{itshape}

Thank you for the comment.
The angle in the figure is meant to match the terminal constraint \( \theta_d\).
In addition, the reachable set is only circular for ease of design in the figure.
In reality the figure will be a general shape, rather than specifically circular.

The manuscript has been modified to correct the figure and also incorporate some more discussion of the figure. 
The additions are included below as well as the updated figure.
\begin{correction}
\Cref{fig:reachability_set} illustrates how, without any control input, trajectories will intersect with the \Poincare section at \( \vecbf{x}_n \). 
However, the addition of low thrust propulsion allows the spacecraft to depart from the natural dynamics and intersect the \Poincare section at a different location.
We use a cost function to define a distance metric on the \Poincare section from the control-free intersection to an intersection under the influence of the control input.
Maximization of this distance along varying directions enables us to generate the largest reachability set under the bounded control input.
In~\cref{fig:reachability_set} the reachable set is shown as a circular region on the \Poincare section.
In practice, the reachable set will be of a general shape and also higher dimensional in the nonplanar case.
\begin{figure}
        \centering
%       \includegraphics[width=0.5\textwidth]{reachability_set_hand}
        \begin{scaletikzpicturetowidth}{0.5\textwidth}
        \begin{tikzpicture}[tdplot_main_coords,
          poincare/.style={opacity=.2,very thick,fill=blue},
          orbit/.style={very thick,black},
          orbit hidden/.style={very thick,dashed},
          grid/.style={very thin,black},
          axis/.style={->,blue,thick},
          reachability/.style={thick,blue},scale=\tikzscale]

        % draw a periodic orbit
        \coordinate (center) at (0,0,2);
        \node[label=below:\(\vecbf{x}_n\)] (x0) at (0,3,2) {};
        % \node[label=below:\(\vecbf{x}_n\)] at (x0) {};
        \filldraw (x0) circle (3pt);

        % \tdplotdrawarc[orbit hidden]{(center)}{3}{90}{200}{}{};
        \tdplotdrawarc[orbit,<-]{(center)}{3}{-160}{90}{}{};

        % draw reachability set on the poincare section
        \coordinate (reach) at (0,4.5,2);
        \tdplotsetthetaplanecoords{90}

        \draw[tdplot_rotated_coords,grid] (x0) -- (reach);
        \draw[tdplot_rotated_coords,grid] (x0) -- ++(-45:1.5);

        \tdplotdrawarc[tdplot_rotated_coords,grid]{(x0)}{0.5}{-45}{90}{above}{\(\theta_d\)};

        % draw terminal state on reachability set
        \node[tdplot_rotated_coords,label=above:\(\vecbf{x}_f\)] (xf) at ($ (x0)+(-45:1.5) $) {};
        \filldraw (xf) circle (3pt);

        \node[tdplot_rotated_coords,label=below:\(J\)] at (xf) {};

        \tdplotdrawarc[tdplot_rotated_coords,reachability]{(x0)}{1.5}{0}{360}{}{};
        % place
    \end{tikzpicture}
        \end{scaletikzpicturetowidth}
        \caption{Reachability set on a \Poincare section: Pictoral representation of the reachability set (blue circle) on the \Poincare section, \(\Sigma\). 
        }
\end{figure}
\end{correction}
\item
    \begin{itshape}
Consider plotting the intersections of manifolds with the Poincare section as continuous curves.  
\end{itshape}

### 2017-07-17 manuscript.tex
Correct reachability plot and add some detail
Reviewer 2 Comment 9

\subsection{Optimal Control Formulation}\label{sec:optimal_control}
In this paper, we seek to approximate the reachability set on a \Poincare section by solving a related optimal control problem. 
We choose our \Poincare section in a similar manner to those used previously for the design of transfers via invariant manifolds.
The \Poincare section is chosen to intersect transversally with trajectories emanating from the initial orbit. 
In the case of a periodic orbit the trajectories will cross the \Poincare section at two distinct fixed points every half period.
The main idea is that the addition of low thrust propulsion allows us to enlarge the set of trajectories achievable in the \Poincare section. 
\Cref{fig:reachability_set} illustrates how, without any control input, trajectories will intersect with the \Poincare section at \( \vecbf{x}_n \). 
However, the addition of low thrust propulsion allows the spacecraft to depart from the natural dynamics and intersect the \Poincare section at a different location.
We use a cost function to define a distance metric on the \Poincare section from the control-free intersection to an intersection under the influence of the control input.
Maximization of this distance along varying directions enables us to generate the largest reachability set under the bounded control input.
\begin{figure}
        \centering
%       \includegraphics[width=0.5\textwidth]{reachability_set_hand}
        \begin{scaletikzpicturetowidth}{0.5\textwidth}
        \begin{tikzpicture}[tdplot_main_coords,
          poincare/.style={opacity=.2,very thick,fill=blue},
          orbit/.style={very thick,black},
          orbit hidden/.style={very thick,dashed},
          grid/.style={very thin,black},
          axis/.style={->,blue,thick},
          reachability/.style={thick,blue},scale=\tikzscale]

@@

        \tdplotdrawarc[tdplot_rotated_coords,grid]{(x0)}{0.5}{-45}{90}{above}{\(\phi\)};

@@

        \tdplotdrawarc[tdplot_rotated_coords,reachability]{(x0)}{1.5}{0}{360}{}{};
        % place
    \end{tikzpicture}
        \end{scaletikzpicturetowidth}
        \caption{Reachability set on a \Poincare section\label{fig:reachability_set}}
\end{figure}

>>>>

\subsection{Optimal Control Formulation}\label{sec:optimal_control}
In this paper, we seek to approximate the reachability set on a \Poincare section by solving a related optimal control problem. 
We choose our \Poincare section in a similar manner to those used previously for the design of transfers via invariant manifolds.
The \Poincare section is chosen to intersect transversally with trajectories emanating from the initial orbit. 
In the case of a periodic orbit the trajectories will cross the \Poincare section at two distinct fixed points every half period.
The main idea is that the addition of low thrust propulsion allows us to enlarge the set of trajectories achievable in the \Poincare section. 
\Cref{fig:reachability_set} illustrates how, without any control input, trajectories will intersect with the \Poincare section at \( \vecbf{x}_n \). 
However, the addition of low thrust propulsion allows the spacecraft to depart from the natural dynamics and intersect the \Poincare section at a different location.
We use a cost function to define a distance metric on the \Poincare section from the control-free intersection to an intersection under the influence of the control input.
Maximization of this distance along varying directions enables us to generate the largest reachability set under the bounded control input.
In~\cref{fig:reachability_set} the reachable set is shown as a circular region on the \Poincare section.
In practice, the reachable set will be of a general shape and also higher dimensional in the nonplanar case.
\begin{figure}
        \centering
%       \includegraphics[width=0.5\textwidth]{reachability_set_hand}
        \begin{scaletikzpicturetowidth}{0.5\textwidth}
        \begin{tikzpicture}[tdplot_main_coords,
          poincare/.style={opacity=.2,very thick,fill=blue},
          orbit/.style={very thick,black},
          orbit hidden/.style={very thick,dashed},
          grid/.style={very thin,black},
          axis/.style={->,blue,thick},
          reachability/.style={thick,blue},scale=\tikzscale]

@@

        \tdplotdrawarc[tdplot_rotated_coords,grid]{(x0)}{0.5}{-45}{90}{above}{\(\theta_d\)};

@@

        \tdplotdrawarc[tdplot_rotated_coords,reachability]{(x0)}{1.5}{0}{360}{}{};
        % place
    \end{tikzpicture}
        \end{scaletikzpicturetowidth}
        \caption{Reachability set on a \Poincare section: Pictoral representation of the reachability set (blue circle) on the \Poincare section, \(\Sigma\). 
        \label{fig:reachability_set}}
\end{figure}
